Data Preparation, Integration and Cleaning

### 2018-05-07 scripts/3_data_prep.Rmd
Move to SF spatial handling

  library(spdep)
  library(maptools)
  library(gstat)
  library(ggplot2)
  library(geosphere)
  library(ggmap)
  library(xtable)
  library(plyr)
  library(sp)
  library(rgeos)
  library(reshape2)
  library(stringr)
  library(RColorBrewer)
  library(Hmisc)
  library(dplyr)
  library(multidplyr)
  library(lubridate)
  library(tidyverse)

@@

  # Suburb shapefile

  suburbs_shp <- readShapePoly(file.path(data_path, 'geographic', 'melbSuburbs.shp'),
                               proj4string=CRS("+init=epsg:4283"),
                               delete_null_obj=TRUE)
  names(suburbs_shp@data) <- tolower(names(suburbs_shp@data))

  # SA1 shapefile

  sa1s_shp <- readShapePoly(file.path(data_path, 'geographic', 'sa1s.shp'),
                            proj4string=CRS("+init=epsg:4283"),
                            delete_null_obj=TRUE)
  names(sa1s_shp@data) <- tolower(names(sa1s_shp@data))

  # Beach file

  beach_shp <- readShapePoly(file.path(data_path, 'geographic','portPhillipBeach.shp'),
                             proj4string=CRS("+init=epsg:4283"),
                             delete_null_obj=TRUE)
  names(beach_shp@data) <- tolower(names(beach_shp@data))

>>>>

  library(spdep)
  library(maptools)
  library(gstat)
  library(ggplot2)
  library(geosphere)
  library(ggmap)
  library(xtable)
  library(plyr)
  library(sp)
  library(rgeos)
  library(reshape2)
  library(stringr)
  library(RColorBrewer)
  library(Hmisc)
  library(dplyr)
  library(multidplyr)
  library(lubridate)
  library(tidyverse)
  library(sf)

@@

  sub_sf <- sf::st_read(file.path(data_path, 'geographic', 'melbSuburbs.shp')) %>%
    st_transform(crs=4283)
  sa1_sf <- sf::st_read(file.path(data_path, 'geographic', 'sa1s.shp')) %>%
    st_transform(crs=4283)
  beach_sf <- sf::st_read(file.path(data_path, 'geographic','portPhillipBeach.shp')) %>%
    st_transform(crs=4283)
